Presentation Title

### 2017-06-21 thesis/chapters/ch2-model.tex
Rewrite proof

$\forall r \in \mathbb{N}$, the following properties must be satisfied.
\begin{enumerate}
    \item \emph{Agreement}:
        If one honest node outputs a list of facilitators $\F_r$,
        every other node honest decides on $\F_r$
    \item \emph{Validity}:
        If any honest node outputs $\F_r$, then $|\F_r| > n$ and $|\F_r|$ must contain at least $n - t$ honest nodes.
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        At the end of the round, every node outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but they have some subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

>>>>

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a list of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ must hold for the $\C_r$ which was used to create $\F_r$,
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but they have some subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

### 2017-06-21 thesis/chapters/ch3-analysis.tex
Write implementation and experiment setup
Rewrite proof

\chapter{Fault Tolerance and Security Analysis}
\label{ch:analysis}

Up to this point we described our system specification in detail.
Of course, specification along does not establish any truths.
In this chapter, we prove two aspects of our system.
First is correctness,
where we show that the consensus protocol and the validation protocol satisfies their desired properties
(\Cref{def:consensus} and \Cref{def:validation} respectively).
The second is performance,
where we prove the lower bound of our throughput and show that it out performs classical blockchain systems.

\section{Correctness in the Presense of Faults}
Our first objective in this section is to establish truths regarding the correctness of our protocol.
We do this in two parts.
First we use mathematical induction to show that properties in \Cref{def:consensus} holds for all round.
Building on top that, if \Cref{def:consensus} is true, then we can show that many properties in \Cref{def:validation} is true.

\subsection{Correctness of Consensus}

We begin our analysis by establishing the fact that the $\textsf{get\_facilitator}(\cdot)$ is fair.
\begin{lemma}
\label{lemma:fairness}
% (Fairness of facilitator election)
Every node with a CP block in $\C_r$, should have an equal probability to be elected as a facilitator.
\end{lemma}
\begin{proof}
This directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_r, || pk_i)$.
Since $pk_i$ is unique for every node that has a CP block in $\C_r$, the output of $\textsf{H}(\cdot)$ is uniformly random.
This implies that the ordered sequence by luck value is uniformly random.
\end{proof}

Using \Cref{lemma:fairness}, we show that our consensus protocol satisfied \Cref{def:consensus}.
\begin{lemma}
\label{lemma:consensus}
% (Correctness of consensus)
$\forall r \in \mathbb{N}$, agreement, validity, fairness and termination holds.
\end{lemma}

\begin{proof}
We proof by mathematical induction.

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol, due to the bootstrap oracle.
Note that the result is $\F_1$, which indicates the facilitators that are agreed in round 1 and are responsible for driving the ACS protocol in round 2.

For the inductive step, we assume that the properties hold for round $r$.
Then, to start round $r + 1$, the honest nodes begin sending CP blocks to $\F_r$. % TODO but they don't send at the same time!
Since the honest region in $\F_r$ waits for $D$ and $D \gg \Delta$,
the CP blocks of the honest nodes are guaranteed to be received by at least $n - t$ facilitators.
The agreement property of ACS (from \Cref{def:acs}) ensures that the $\C_{r + 1}$ is in consensus. 
Observe that $\F_{r + 1}$ is computed using the deterministic function $\textsf{get\_facilitators}(\cdot)$.
Thus agreement of $\F_{r + 1}$ follows directly from the agreement of ACS.
The validity property of ACS ensures that $\C_{r + 1}$ contains the input of at least $n - 2t$ parties, but this is a quorum containing at least one honest facilitator,
thus $\C_{r + 1}$ contains the CP blocks of all nodes.
Due to the assumption that the adversary cannot corrupt more than $t$ nodes,
validity of $\F_{r + 1}$ also follows from validity of ACS.
Since all honest nodes are in $\C_{r + 1}$, the fairness property follows directly from \Cref{lemma:fairness}.
Finally, the termination property holds because $D$ eventually elapses and then ACS eventually terminates
(the totality property of ACS).
This completes the proof.
\end{proof}

\subsection{Correctness of Validation}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{lemma:consensus} to show that most properties in \Cref{def:validation} can be satisfied.

@@

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}
We proof by contradiction.
Without loss of generality, for some transaction $t$ with an agreed fragment $F$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exist a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exist a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ must have reached \Cref{line:valid-fragment}.
Due to \Cref{lemma:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, the sender of $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But we assumed that the adversary can only perform polynomial-time algorithm, but in order to find $t''$ it needs to query the random oracle exponentially many times.
Thus we have a contradiction and this completes our proof.
\end{proof}

\Cref{theorem:validation-agreement} is our first major result.
It shows that consensus on CP blocks would lead to consensus on TX blocks when the nodes are running the validation protocol.
One of the main advantages over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS (up to $L$ transactions).
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

However, not everything is perfect.
Now we show a negative result, where the liveness property cannot be attained.
\begin{lemma}
There exist a valid transactions that cannot be validated eventually.
\end{lemma}
\begin{proof}
We proof by providing a counterexample.
Suppose nodes $u$ and $v$ correctly perfomed the TX protocol which resulted a transaction $t$.
Then when $u$ wants to validate $t$, it does so by sending \texttt{vd\_req} message to $v$.
$v$ can act maliciously and ignore all \texttt{vd\_req} message, thus $t$ can never be validated.
\end{proof}
Although this is a negative result, it does not put the adversary in an advantageous position.
If the adversary is observed to ignore validation requests, then the honest nodes may prefer not to transact with her in the future.
Thus, to stay relevant in the system, the adversary need to comply to the protocol.

@@

>>>>

\chapter{Analysis of Correctness and Performance}
\label{ch:analysis}

Up to this point we described our system specification in detail.
Of course, specification along does not establish any truths.
In this chapter, we analyse two aspects of our system.
First we show it has the desired properties.
That is, the properties in \Cref{def:consensus} and \Cref{def:validation} should hold.
Then we analyse the performance, especially the throughput,
and show that it out performs classical blockchain systems.

\section{Correctness in the Presense of Faults}
Our first objective is to show that \Cref{def:consensus} holds for our consensus protocol.
Then, building on top of it, we show \Cref{def:validation} holds for the validation protocol.
The resulting theorem shows that only using CP blocks in the consensus algorithm implies consensus on TX blocks,
in other words, implicit consensus.

% Our first objective in this section is to establish truths regarding the correctness of our protocol.
% We do this in two parts.
% First we use mathematical induction to show that properties in \Cref{def:consensus} holds for all round.
% Building on top that, if \Cref{def:consensus} is true, then we can show that many properties in \Cref{def:validation} is true.

\subsection{Analysis of the Consensus Protocol}

We begin our analysis by establishing truths on the four properties in \Cref{def:consensus},
namely agreement, validity, fairness and termination.
Using these results, we use mathematical induction to show that they hold for all rounds.

\begin{lemma}
\label{lemma:agreement}
For an arbitrary round $r$
if $\F_{r}$ is known by all correct nodes and one correct node outputs a list of facilitators $\F_{r+1}$,
then all correct nodes output $\F_{r+1}$.
\end{lemma}
\begin{proof}
The argument follows from the protocol description.
Given that $\F_r$ is known,
correct nodes will send CP blocks to all members in $\F_r$.
The ACS algorithm starts independently whenever the facilitator has $N - t$ valid CP blocks
(recall from \Cref{sec:consensus-phase} that invalid blocks are ones with an invalid signature or has a duplicate signature).
It cannot make progress until $n-t$ honest facilitators start algorithm,
but this eventually happens because there are $N - t$ correct nodes and all correct facilitator eventually receives $N -t$ valid CP blocks.
At the end of ACS, some $\C_{r+1}$ is created, and is broadcasted along with the signature of the facilitators.
Due to the agreement property of ACS (\Cref{def:acs}),
every correct node should receive at least $n - t$ valid signatures on the agreed $\C_{r+1}$.
Thus they use $\C_{r+1}$ to generate a new CP block and compute new facilitators.
Since $\textsf{get\_facilitators}(\cdot)$ is a deterministic algorithm and the input $\C_{r+1}$ is in agreement, the output $\F_{r+1}$ is also in agreement.
\end{proof}

\begin{lemma}
\label{lemma:validity}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes and any correct node outputs $\F_{r+1}$,
then (a) $|\C_{r+1}| \ge N - t$ must hold for the $\C_{r+1}$ which was used to create $\F_{r+1}$,
(b) $\F_{r+1}$ must contain at least $n - t$ honest nodes and
(c) $|\F_{r+1}| = n$.
\end{lemma}
\begin{proof}
The validity follows from the validity property of ACS and the definition of our model,
namely $N \ge n + t$ and $n \ge 3t + 1$.
Given $\F_r$, since $N \ge n + t$ , there is at least $n$ nodes that would send their CP block to $\F_r$.
From the validity property of ACS, we know the output must contain the input of at least $n - 2t$ nodes.
But $n -t$ facilitators must have received $N - t$ valid CP blocks, so $|\C_{r+1}| \ge N-t$, this proves (a).
There are $n-t$ honest nodes in $\F_{r+1}$ follows from the model, this proves (b).
Finally, since $N-t \ge (n+t) -t = n$ and $\textsf{get\_facilitators}(\cdot)$ outputs $n$ items, $|\F_{r+1}| = n$ and this proves (c).
\end{proof}

\begin{lemma}
\label{lemma:fairness}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every node with a CP block in $\C_{r+1}$, should have an equal probability to be elected as a facilitator in $\F_{r+1}$.
\end{lemma}
\begin{proof}
We have already established that $|\C_{r+1}| \ge N - t \ge n$ from \Cref{lemma:validity}.
Then the proof directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_{r+1}, || pk_u)$.
Since $pk_u$ is unique for every node that has a CP block in $\C_{r+1}$,
the output of $\textsf{H}(\cdot)$ is uniformly random.
This effectively generates a random permutation
so every node has the same probability of being in the top $n$ for the ordered sequence,
namely the output of $\textsf{get\_facilitators}(\cdot)$.
\end{proof}

\begin{lemma}
\label{lemma:termination}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every correct node eventually outputs some $\F_{r + 1}$.
\end{lemma}
\begin{proof}
This follows directly from the properties of the channel (eventual delivery)
and the termination property of ACS.
That is, $\F_r$ eventually receives all the CP blocks required to begin ACS.
ACS eventually terminates.
Finally the results are eventually dissemminated to all the nodes.
\end{proof}

From Lemmas \ref{lemma:agreement}, \ref{lemma:validity}, \ref{lemma:fairness} and \ref{lemma:termination},
we have shown that the 4 properties of \Cref{def:consensus} holds when assuming the existance of some $\F_r$.
Thus, to proof the whole of \Cref{def:consensus},
we need to proof these 4 properties under the universal quantifier.
We do this using mathematical induction.

\begin{theorem}
\label{theorem:consensus}
For all rounds,
the consensus protocol satisfies agreement, validity, fairness and termination (\Cref{def:consensus}).
\end{theorem}
\begin{proof}
We proof using mathematical induction.

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol,
due to the bootstrap oracle.
Note that the result is $\F_1$, which indicates the facilitators that are agreed in round 1, who are responsible for driving the ACS protocol in round 2.

For the inductive step,
we assume that the 4 properties hold in round $r$ and prove that they also hold in round $r + 1$.
Using Lemmas \ref{lemma:agreement}, \ref{lemma:validity}, \ref{lemma:fairness} and \ref{lemma:termination},
it directly follows from Modus Poneus that these properties hold for $r + 1$.
Due to the principals of mathematical induction, these properties hold for all $r$.
\end{proof}

\subsection{Correctness of Validation}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{theorem:consensus} to show that most (except liveness) properties in \Cref{def:validation} can be satisfied.

@@

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}
We proof by contradiction.
Without loss of generality, for some transaction $t$ with an agreed fragment $F$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exist a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exist a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ function must have reached \Cref{line:valid-fragment}.
Due to \Cref{theorem:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, whoever sent $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But we assumed that the adversary can only perform polynomial-time algorithm,
so in order to find $t''$ it needs to query the random oracle exponentially many times.
Thus we have a contradiction and this completes the proof.
\end{proof}

\Cref{theorem:validation-agreement} is our first major result.
It shows that consensus on CP blocks would lead to consensus on TX blocks when the nodes are running the validation protocol.
Just like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

\subsection{Impossibility of Liveness}
While \Cref{theorem:validation-agreement} is a major result that allows significantly improved performance over traditional blockchain systems,
it is not perfect.
Now we show a negative result, where the liveness property of \Cref{def:validation} cannot be attained.
Meaning that trasanctions with adversaries cannot always be validated.

\begin{lemma}
There exist a valid transactions that cannot be validated eventually.
\end{lemma}
\begin{proof}
We proof by providing a counterexample.
Suppose nodes $u$ and $v$ correctly perfomed the TX protocol which resulted a transaction $t$.
Then when $u$ wants to validate $t$, it does so by sending \texttt{vd\_req} message to $v$.
$v$ can act maliciously and ignore all \texttt{vd\_req} message, thus $t$ can never be validated.
\end{proof}
Although this is a negative result, it does not put the adversary in an advantageous position.
If the adversary is observed to ignore validation requests, then the honest nodes may prefer not to transact with her in the future.
Thus, to stay relevant in the system, the adversary need to comply to the protocol.

@@

\section{Effect of A Highly Adverserial Environment}
